Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Splitted sentences in manuscript
Modified Methodology in manuscript

From equation \ref{eq:glq-var-dens} we can conclude that the error of 
the numerical approximation is controlled by the order of the 
quadrature, i.e. the number of point masses that are going to be used 
to compute the gravitational field.
This conclusion could lead to a naive methodology: find the order of 
the quadrature that produces gravitational fields with an acceptable 
accuracy.
Although this simple proposal has a few problems: (a) it won't be 
efficient and (b) it couldn't be applied to the general case (any
tesseroid with arbitrary density function on any computational point) 
without modifying the quadrature order taking into account 
characteristics of the tesseroid and the computation point (tesseroid 
size, distance to the computation point, variation of the density 
function, etc).

That's why we will keep the GLQ order fixed and make use of 
discretization algorithms.
Instead of uniformly increase the number of point masses that 
approximates a certain tesseroid, the discretization algorithms are 
intended to efficiently subdivide the tesseroid into smaller ones and 
apply the GLQ to each one of them.
These algorithms generally involve a discretization inequation that 
controls if the tesseroid should be subdivided or not and a certain 
predefined parameter that works as a threshold for the discretization 
inequation.

On the variable density tesseroid problem we found two main error 
sources in the GLQ that should be addressed: (a) the relation between 
the tesseroid size and its distance to the computation point, and (b) 
the variation of the density function.

>>>>

In a general way, the numerical error of the GLQ is controlled by the 
order of the quadrature: a higher GLQ order produces a more accurate 
approximation \citep{Hildebrand1987}.
This can also be understood in terms of the tesseroid problem: a higher 
quadrature order increases the number of point masses used to compute 
the gravitational fields and thus lowers the numerical error.

This reasoning could lead to a naive methodology in order to ensure 
accurate gravitational field computations: find the order of the 
quadrature that produces an acceptable numerical error.
Nevertheless, this simple proposal has a few problems: (a) it won't be 
efficient \citep{Li2011, Uieda2016} and (b) it couldn't be applied to 
the general case, i.e. the needed quadrature order probably won't be 
the same for every tesseroid, computation point or density function.

That's why we will keep the GLQ order fixed and make use of 
discretization algorithms.
Instead of uniformly increase the number of point masses that 
approximates a certain tesseroid, the discretization algorithms are 
intended to efficiently subdivide the tesseroid into smaller ones and 
apply the GLQ to each one of them.
These algorithms generally involve a discretization inequation that 
controls if the tesseroid should be subdivided or not, and a certain 
predefined parameter that works as a threshold for the discretization 
inequation.

On the variable density tesseroid problem we found two main error 
sources in the GLQ that should be addressed: (a) the ratio between 
the tesseroid size and its distance to the computation point, and (b) 
the variation of the density function.
